---
title: "140SL_Midterm1"
author: "Seulchan Kim"
date: '2019 11 1 '
output: html_document
---

```{R, echo=FALSE}
library(ggplot2)
library(tidyr)
library(MASS)
library(readxl)
library(readr)
library(leaps)
library(tibble)
library(dplyr)
library(readxl)
library(ggplot2)
```

```{r}
data<-read_excel("codebook4PMA.xls", sheet = 2)
data2<-read_excel("codebook4PMA.xls")
# healthy BMI: 18.5-24.9 inclusive
# unhealthy BMI is otherwise(18.5 or greater than 24.9)
```


```{r}
data <- data %>% mutate(A18 = replace(`A18`, `A18` > 87, NA))
data <- data %>% mutate(A19 = replace(`A19`, `A19` > 87, NA))

data <- data %>% mutate(BMI= ( data$A19 / (data$A18)^2 ))

cleaned_data <- data %>% filter(!is.na(A19) & !is.na(A18))
cleaned_data

health_data <- data %>% mutate(health = (data$BMI >= 18.5 & data$BMI <= 24.9))

health<- health_data %>% filter(health ==1)
unhealth <- health_data %>%filter(health ==0)

```


1. Please generate a demographic profiles of the students with healthy and also for students with unhealthy BMI. Just a few simple tabulations or summary statistics will be sufficient.

```{r}
mean(health$A19)
mean(unhealth$A18)

summarise_all(health_data, funs(mean), na.rm = TRUE)
summarise_all(health_data, funs(min), na.rm=TRUE)

health %>% summarise(meanage = mean(A19, na.rm = T),meansex = mean(A18,na.rm = T), meanBMI = mean(BMI,na.rm = T))
unhealth %>% summarise(meanage = mean(A19, na.rm = T),meansex = mean(A18,na.rm = T), meanBMI=mean(BMI,na.rm = T))

```



2. Please create a graphic/visualization (just one good one is sufficient) which reveals any association between BMI and any of the other variables in the dataset. Hint: take the time to sketch a graphic, then create it.

```{r}
ggplot(data=health_data, aes(x=factor(A3), y=BMI)) + geom_boxplot() + xlab('Age')
ggplot(data=health_data, aes(x=factor(A1), y=BMI)) + geom_boxplot() + xlab('Gender')
ggplot(data=health_data, aes(x=factor(A2), y=BMI)) + geom_boxplot() + xlab('Grade')
ggplot(data=health_data, aes(x=factor(A16), y=BMI)) + geom_boxplot() + xlab('Tobacco')
ggplot(data=health_data, aes(x=factor(A6), y=BMI)) + geom_boxplot() + xlab('Drinks past 30 days')
```



3. If you were to attempt to model BMI (either as a numeric variable or a binary variable) as a dependent variable with any of the other variables serving as independent variables, please describe (in English please, R and Python don’t count here) the process and set up a model.


```{r}
m <- lm(BMI ~ A3 + A1 + A2 + A16 + A6, 
         data=cleaned_data)
anova(m)
summary(m)
```

```{r}
m2 <- lm(BMI ~., data = cleaned_data)
anova(m2)
summary(m2)
```


